Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-04-16 MUSES_vs_BYOD_solutions.tex
First para intro with comments for @unintendedbear: more references

The way on how data has been stored and accessed in the companies has completely changed along the years. The use of owned servers being accessed by desktop PCs (and maybe laptops) from inside the company facilities has been transformed into the distribution of these data between a number of machines, even not all belonging to the company, and working over the famous Cloud Computing environment. Besides, being stored in the cloud or not, data are being consulted and modified through a wide amount of devices, some of them owned by the company's users. This is the so-called Bring Your Own Device (BYOD) philosophy. It is becoming highly successful due to the impact that portable devices (such as smartphones and tablets) are having on the market.
Data security and privacy are key factors for a company, thus, to protect them, it is usual to define Organisational Security Policies. Their definition is nowadays a very difficult problem, since the BYOD tendency means that several factors must be considered \cite{Opp_Security11}, most of them previously ignored or non considered in security systems. For instance, the current mixture between personal and professional information in these devices (the user could navigate inside social networks where there could be friends and also company partners or clients).

>>>>

The way on how data has been stored and accessed in companies has
completely changed along the last years. The scenario where
company-owned servers are being accessed by desktop PCs (and maybe
laptops) from inside the company facilities has been transformed into
another where data, increasingly a company asset, is distributed
between a number of machines, maybe not all owned by the company, and
working on the famous Cloud. Besides, being
stored in the cloud or not, data is being consulted and modified
through a wide variety of devices, some of them owned by the company's
employees, in what is called the Bring Your Own Device (BYOD)
philosophy. This philosophy has become highly successful due to the impact that
portable devices (such as smartphones and tablets) are having on the
market. % There should be a reference for this - JJ
Data security and privacy are key factors for a company, thus, to protect them, it is usual to define Organisational Security Policies. Their definition is nowadays a very difficult problem, since the BYOD tendency means that several factors must be considered \cite{Opp_Security11}, most of them previously ignored or non considered in security systems. For instance, the current mixture between personal and professional information in these devices (the user could navigate inside social networks where there could be friends and also company partners or clients).
